Draft

### 2016-07-10 draft.tex
Notes on The Mathematical Theory of Communication by Shannon. Very interesting article.

    Density matrix satisfies several good properties:
    \begin{itemize}
        \item Normalized
        \item Hermiticity
        \item Positivity. For any $\Phi$, $\braket{\Phi|\rho|\Phi} \geq 0$.
    \end{itemize}
\section{Anchor}
% This is just an anchor for seperating thebibliography from above contents.
\begin{thebibliography}{1}
	\bibitem{Sakurai} Sakurai, J. J. Modern Quantum Mechanics, Addison Wesley.
	\bibitem{BSCS} Bosonization and Strongly Correlated Systems. Cambridge.

>>>>

    Density matrix satisfies several good properties:
    \begin{itemize}
        \item Normalized
        \item Hermiticity
        \item Positivity. For any $\Phi$, $\braket{\Phi|\rho|\Phi} \geq 0$.
    \end{itemize}
    \subsection{The Mathematical Theory of Communication}
    \label{sec:The_Mathematical_Theory_of_Communication}
    \subsubsection{Introduction}

    \paragraph{What is information}
    In this part, it is implied that \textit{information} in this work
    does not carry the usual sense in people's daily life. The semantic
    aspect of a message is considered to be irrelavant, for purpose
    of generality of the design of communication systems.

    \paragraph{Measure of information} 
    % TODO Read the paper of Hartley to understand what is information:
    % Hartley, R. V. L., "Transmission of Information," Bell System Technical
    % Journal, July 1928, p. 535

    Then it refers to a paper by Hartley to substantiate the use of
    \begin{align}
        \label{eq:measure_of_information}
        S = \log(M)
    \end{align}
    as a measure of information. More specifically, we assume we have a
    set of possible messages. Then $M$ is the cardinality of this set.
    Then $S$ is a measure of the information produced when one message
    is chosen from the set. Once again, we regard all choices 
    being equally possible.

    Note that the base of logrithm in \ref{eq:measure_of_information}
    is undefined. Choosing a base constituting choosing a unit of
    the measure. Two such measures, when calculated in different units,
    are related by a simple constant.

    Conventionally, a base $2$ is chosen. The resulted unit is called
    bits. If the base $10$ is chosen, then the units may be called
    decimal digits. If the base $e$ is chosen, then the units is
    called natural units.

    Also, the author lists several points to illustrate the
    convenience of this measure.

    \paragraph{Communication systems}
    Next the author defines the necessary components of a \textit{
    communication system}, and categorizes it into discrete systems,
    continuous systems and mixed systems.

    \subsubsection{Discrete Noiseless Systems}

    \paragraph{Discrete Noiseless Channel}
    \label{sec:Discrete Noiseless Channel}
    This part deals with another measure, the measure of the capacity
    of a channel to transmit information. It defines the capacity of a
    discrete channel as:
    \begin{align}
        \label{eq:capacity_of_disc_chan}
        C\equiv \lim_{T\to \infty} \frac{\log N(T)}{T}
    \end{align}
    where $N(T)$ is the number of allowed signals of duration $T$.
    Several examples are given with formula for $C$ in each particular
    example.

    \paragraph{Discrete Source of Information}
    Next, it proceeds to discuss the statistical property of the source
    of information. Pointing out that a statistical knowledge of the
    source of information can help peopole craft special protocals to
    reduce the required capacity of the channel, the article gradually
    focuses on the statistical property of sourcs. It profess that while a
    discrete source could be represented by a statistical source, a
    statistical process can also be considered a discrete source. The
    second claim is substatiated by several exmaples.

    In one example of natural language, the article defines a 
    \textit{n-gram} case to produce natural language from statistical
    information.

    \paragraph{Series of Approximations to English}
    As the title suggests, this part illustrate two serial levels of
    steps to approximate the English language using statistical knowledge
    of appearance of alphabets (the first method) and words (the second
    example). The article claims that "a sufficiently complex stochastic 
    process will give a satisfactory representation of a discrete source".
    Although I am largely against this juvenile view.

    \paragraph{Graphical Representation of a Markoff Process}
    Then the article mentions a graphical way to represent the aforementioned
    approximation process, and gives three examples on page 46.

    \paragraph{Ergodic and Mixed Sources}
    Now the article comes to a special type of stochastic process, ergodic
    processes. A rough idea of "ergodic" is given in page 45. The idea is
    so important that I felt compeled to present it here:

    "In an ergodic process every sequence produced by
    the process is the same in statistical properties. Thus the letter
    frequencies, digram frequencies, etc., obtained from particular
    sequences, will, as the lengths of the sequences increase, approach
    definite limits independent of the particular sequence.
    Actually
    this is not true of every sequence but the set for which it is false
    has probability zero. Roughly the ergodic property means 
    \textbf{statistical homogeneity}."

    Next, the article claims that artificial languages given in previous
    examples are ergodic, because the corresponding graph does not
    have two properties: they does not comprise two or more \textit{isolated
    parts}, and they $gcd$ of the lengths of all \textit{circuits }is one.
    The precise meaning is listed in page 47. Roughly, an analogy made by
    myself helps to
    catch the points. If we picture an stochastic process as a connected 
    area, then isolated parts are its connected components, whereas the
    circuit are the recurrent pattterns.

    Naturally , a stochastic process may exhibit a mixed behavir, in which
    there are several different sources $L_1,L_2,L_3,\cdots$, which are
    each of homogeneous, i.e. ergodic, statistical structure. This is
    discussed following the introduction of ergodicity in page 48.

    Then the article declare that except in special cases, ergodicity is
    always assumed. This purpose is analogous to that of in statistical
    physics, to "identify averages along a sequence with averages over 
    the ensemble of possible sequences", with "the probability of a
    discrepancy being zero".

    Lastly, the article mentions a fact regarding the equilibrium of
    the system. A process is called stationary, if it satisfies a
    equilibrium condition:
    \begin{align}
        \label{eq:Ergodic_and_Mixed_States:equil_condition}
        P_j = \sum_i P_i \cdot P_i(j)
    \end{align}
    where $P_j$ is the probability of being in state $j$, and $P_i(j)$ is
    the transition probability from $i$ to $j$.
    The fact is that ergodic process is, in a sense, always stationary.

    \paragraph{The Entropy of an Information Source}
    This part first defines the entropy of a discrete source of finite state
    to be:
    \begin{align}
        \label{eq:entropy_of_discrete_infor_source}
        H \equiv& \sum_i P_i H_i\\
        =& -\sum_{i,j} P_i p_i(j) \log(p_i(j)) \nonumber
    \end{align}
    It is "the entropy of the source per symbol of text". Another
    definition for entropy per second is also listed.

    Following this definition are some theorems, which I consider to be
    the most essential and influential part of the whole book (although
    I have not yet read the whole book). They are:

    \begin{thm}[Theorem 3 on page 55]
        Given any $\epsilon >0$ and $\delta >0$, we can find an $N_0$
        such that the sequences of any legnth $N\geq N_0$ fall into
        two class:
        \begin{itemize}
            \item A set whose total probability is less than $\epsilon$.
            \item The remainder, all of whose members have probabilities
                satisfying the inequality
                \begin{align}
                    \label{eq:Entropy_of_info_source:thm3}
                    \left| \frac{\log p^{-1}}{N}-H\right| < \delta
                \end{align}
        \end{itemize}
    \end{thm}
    "In other words we are almost certain to have 
    $\frac{\log p^{-1}}{N}$ very close to $H$ when $N$ is large."
    For me, this reads quite like the \textit{second law of
    thermaldynamics}.

    % TODO having trouble understanding the Theorem 4 on page 55.

\section{Anchor}
% This is just an anchor for seperating thebibliography from above contents.
\begin{thebibliography}{1}
	\bibitem{Sakurai} Sakurai, J. J. Modern Quantum Mechanics, Addison Wesley.
	\bibitem{BSCS} Bosonization and Strongly Correlated Systems. Cambridge.
